Process_OlisJazEmData

### 2024-01-08 Code/Process_OlisJazEmData.Rmd
removed redundant libraries

```{r load libraries, warning = FALSE, echo=FALSE} 
library(tidyverse)
library(lubridate)
# library(stringr)
library(broom)
library(knitr)
# library(OneR)
library(zoo)
# library(strucchange)
# library(ggspectra)
# library(ggpubr)
# library(caret)
library(photobiologyWavebands)
# library(reshape2)
# library(photobiology)
# library(gcookbook)
```

>>>>

```{r load libraries, warning = FALSE, echo=FALSE}

library(tidyverse)
library(lubridate)
library(broom)
library(knitr)
library(zoo)
library(photobiologyWavebands)
